Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2): Submission, Peer-Review, and Sorting Process, and Results

### 2014-10-13 WSSSPE2_preworkshop_report/WSSSPE2_review_report.tex
addressing Manish's email comment

\begin{abstract}
This technical report discusses the submission and peer-review process used by the Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2) and the results of that process.  It is intended to record both the alternative review model used by WSSSPE2 as well as the papers associated with the workshop that resulted from that process.
\end{abstract}

>>>>

\begin{abstract}
This technical report discusses the submission and peer-review process used by the Second Workshop on on Sustainable Software for Science: Practice and Experiences (WSSSPE2) and the results of that process.  It is intended to record both the alternative submission and program organization model used by WSSSPE2 as well as the papers associated with the workshop that resulted from that process.
\end{abstract}
